Latentcor: An R Package for Latent Correlation Estimation

### 2021-05-30 paper/paper.Rmd
Adding content on paper

---
# Example from https://joss.readthedocs.io/en/latest/submitting.html
title: 'Latentcor: An R Package for Latent Correlation Estimation'
tags:
  - R
  - Statistics
  - Latent Correlation
authors:
  - name: Mingze Huang
    orcid: 0000-0003-3919-1564
    affiliation: "1, 2" # (Multiple affiliations must be quoted)
  - name: Irina Gaynanova
    orcid: 0000-0000-0000-0000
    affiliation: 2
  - name: Christian L. Muller
affiliations:
 - name: Department of Statistics, Texas A& M University
   index: 1
 - name: Department of Economics, Texas A& M University
   index: 2
 - name: Department of Statistics, University of Munich
   index: 3
date: 18 May 2021
year: 2021
bibliography: paper.bib
output: rticles::joss_article
csl: apa.csl
journal: JOSS
---

@@

# Mathematics

# Citations

>>>>

---
title: 'Latentcor: An R Package for Latent Correlation Estimation'
tags:
- R
- Statistics
- Latent Correlation
date: "18 May 2021"
output:
  rticles::joss_article: default
  rticles::joss_article(): default
authors:
- name: Mingze Huang
  orcid: 0000-0003-3919-1564
  affiliation: 1, 2
- name: Irina Gaynanova
  orcid: 0000-0000-0000-0000
  affiliation: 2
- name: Christian L. Muller
year: 2021
bibliography: paper.bib
affiliations:
- name: Department of Statistics, Texas A& M University
  index: 1
- name: Department of Economics, Texas A& M University
  index: 2
- name: Department of Statistics, University of Munich
  index: 3
csl: apa.csl
journal: JOSS
---

@@

The R package *latentcor* provides estimation for latent correlation with mixed data types (continuous, binary, truncated and ternary). Comparing to *MixedCCA*, which estimates latent correlation for canonical correlation analysis, our new package provides a standalone version for latent correlation estimation. Also we add new functionality for latent correlation between ternary/continous, ternary/binary, ternary/truncated and ternary/ternary cases.
Compare to MixedCCA, standalone, new functionality, memory footprint.

# Statement of need
No package deal with latent correlation across mixed data type.

# Usage
 Create a table
 type of variable (reference to papers)
 Definition for Kendall tau.
 Describe the theorem states expected value of kendall tau = F(r). refer to table for reference of formula.
 A sentence to describe two methods: slow original vs interpolation.
 Table to show memory improvement compare to mixedCCA.
 Generate data for pairs.
 One example of original call, one for interpolation call.
# Citations

### 2021-05-30 paper/paper.tex
Adding content on paper

\hypertarget{mathematics}{%
\section{Mathematics}\label{mathematics}}

\hypertarget{citations}{%
\section{Citations}\label{citations}}

>>>>

The R package \emph{latentcor} provides estimation for latent
correlation with mixed data types (continuous, binary, truncated and
ternary). Comparing to \emph{MixedCCA}, which estimates latent
correlation for canonical correlation analysis, our new package provides
a standalone version for latent correlation estimation. Also we add new
functionality for latent correlation between ternary/continous,
ternary/binary, ternary/truncated and ternary/ternary cases. Compare to
MixedCCA, standalone, new functionality, memory footprint.

\hypertarget{statement-of-need}{%
\section{Statement of need}\label{statement-of-need}}

No package deal with latent correlation across mixed data type.

\hypertarget{usage}{%
\section{Usage}\label{usage}}

Create a table type of variable (reference to papers) Definition for
Kendall tau. Describe the theorem states expected value of kendall tau =
F(r). refer to table for reference of formula. A sentence to describe
two methods: slow original vs interpolation. Table to show memory
improvement compare to mixedCCA. Generate data for pairs. One example of
original call, one for interpolation call. \# Citations
